---
title: 'The importance of reproducible research'
author: "Gabriel Nakamura"
date: "5/17/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

In this section you will find a few articles on the importance of adopting a reprodcucible workflow to your research project. From the individual perspective reproducibility helps you with self-organization. From the research community perspective reproducibility helps everyone to push forward the boundaries of science by facilitation the colaboration.

# Suggested literature

- [Perkel, Jeffrey. Democratic databases: Science on GitHub. 2016. Nature](https://www.nature.com/news/democratic-databases-science-on-github-1.20719)
- [Five concrete reasons your students should be learning to analyzing data in a reproducible way](https://chance.amstat.org/2014/09/reproducible-paradigm/)
- [Publish your computer code: it is good enough](https://www.nature.com/news/2010/101013/pdf/467753a.pdf)

# Important packages

Here you can find some important packages that we will use during this course

```{r echo=TRUE, eval=FALSE}
packages <- c("devtools", "rmarkdown", "here", "usethis")
lapply(packages, function(x) install.packages(x))

```
